DataSet 2- Fifa 2018

Loading the Dataset from Drive
```{r}

Fifa18Data <- read.csv("C:\\Users\\SUMEET\\OneDrive\\Project Dataset\\R\\For Dataset 2\\fifa-18-demo-player-dataset\\CompleteDataset.csv", 
                        header = T, na.strings = "", stringsAsFactors = F)
# View(Fifa18Data)

```
Removing the Skills of a player which is for example lie 78+2 or 88-1.
Removing columns that are not required fro the analysis and begening the cleaning.
```{r}


Fifa18Data <- as.data.frame(Fifa18Data) #converting into data frame as tibble doesnt give appropriate results for sub function

for (i in 14:47) # Converting columns with player attributes to numeric
{
  Fifa18Data[,i] <- sub("\\+.*", "", Fifa18Data[,i])
  Fifa18Data[,i] <- sub("\\-.*", "", Fifa18Data[,i])
  
}
Fifa18Data <- as_tibble(Fifa18Data)
# View(Fifa18Data)
```
#Converting into numeric the values which can be char.
```{r}


for (i in 14:47) # Converting columns with player attributes to numeric
{
  Fifa18Data[,i] <- as.numeric(unlist(Fifa18Data[,i] ))
}

```
Removing the unnecessary columns from the data.
```{r}
library(dplyr)
Fifa18DataColClean <- Fifa18Data[,-c(1,2,4,5,6,10,13,54)]#46 column after this to be removed
# View(Fifa18DataColClean)
```

So now we will start Cleaning the Dataset and Remove the ---- values from the Value, Wage of the data set.
```{r}
# install.packages("gsub")
library(gsubfn)
Fifa18DataColClean$Value <- gsub('[€]','',Fifa18DataColClean$Value)
```


```{r}

Fifa18DataColClean$Wage <- gsub('[€]','',Fifa18DataColClean$Wage)
# View(Fifa18DataColClean)


```

```{r}

library(stringr)

Fifa18DataColClean <- Fifa18DataColClean %>% mutate(multiplier = ifelse(str_detect(Value, "K"), 1000, ifelse(str_detect(Value, "M"), 1000000, 1))) 

Fifa18DataColClean <- Fifa18DataColClean %>% mutate(Value = as.numeric(str_extract(Value, "[0-9]+")) * multiplier)
# View(newdataFifa)
Fifa18DataColClean <- Fifa18DataColClean %>% mutate(multiplier = ifelse(str_detect(Wage, "K"), 1000, ifelse(str_detect(Wage, "M"), 1000000, 1))) 

Fifa18DataColClean <- Fifa18DataColClean %>% mutate(Wage = as.numeric(str_extract(Wage, "[0-9]+")) * multiplier)
```
Finding and removing the NA values from the Data
As we have got a large number of columns so now we will group together those columns who will help getting position of the any player.
```{r}
Fifa18DataColClean<- na.omit(Fifa18DataColClean)
# View(Fifa18DataColClean)

Fifa18DataColClean$Skill <- as.numeric(as.character(Fifa18DataColClean$Crossing + Fifa18DataColClean$Acceleration +Fifa18DataColClean$Aggression + Fifa18DataColClean$Agility + Fifa18DataColClean$Balance + Fifa18DataColClean$Ball.control + Fifa18DataColClean$Composure + Fifa18DataColClean$Crossing + Fifa18DataColClean$Curve + Fifa18DataColClean$Curve + Fifa18DataColClean$Dribbling + Fifa18DataColClean$Finishing + Fifa18DataColClean$Free.kick.accuracy + Fifa18DataColClean$Heading.accuracy + Fifa18DataColClean$Interceptions + Fifa18DataColClean$Jumping + Fifa18DataColClean$Long.passing + Fifa18DataColClean$Marking + Fifa18DataColClean$Penalties + Fifa18DataColClean$Positioning + Fifa18DataColClean$Reactions + Fifa18DataColClean$Short.passing + Fifa18DataColClean$Shot.power + Fifa18DataColClean$Sliding.tackle + Fifa18DataColClean$Sprint.speed + Fifa18DataColClean$Stamina + Fifa18DataColClean$Standing.tackle + Fifa18DataColClean$Strength + Fifa18DataColClean$Vision + Fifa18DataColClean$Volleys ))/30
# View(Fifa18DataColClean)
```
Now removing the various Skills of players and also removing the GK skill as we will be identifying three positions only.
DataFifa18 = removed columns
```{r}
DataFifa18 <- Fifa18DataColClean[,-c(7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37)]

names(DataFifa18)
# View(DataFifa18)
```

Converting Positions into Forward, Midfielder and Defender.
Fifa18Data1 = storing the positions

Cleaning and removing more columns that are used
Fifadata18Set = removed columns
```{r}
# 
# Fifadata18Set <- Fifa18Data1[,-c(7,8,9,15,26)]
# View(Fifadata18Set)
# Fifadata18Set$PreferedPosition <- as.factor(Fifadata18Set$PreferedPosition)
# levels(Fifadata18Set$PreferedPosition)
# levels(Fifadata18Set$PreferedPosition)

DataFifa18 <- tidyr::separate(DataFifa18, Preferred.Positions, c("PreferredPosition"), sep = " ", remove = FALSE)

names(DataFifa18)
DataFifa18 <- DataFifa18[ , -c(25)]

table(DataFifa18$`PreferredPosition`)

```
Now Putting the Position of players into one set, for example :- Forward will have ST,LS,RS,LW,RW
```{r}
# install.packages("rockchalk")
library(rockchalk)
table(DataFifa18$PreferredPosition)
DataFifa18$PreferredPosition <- as.factor(DataFifa18$PreferredPosition)

DataFifa18$PreferredPosition <- combineLevels(DataFifa18$PreferredPosition, c("ST", "LW", "RW" ,"CF"), newLabel = 'Forward')
DataFifa18$PreferredPosition <- combineLevels(DataFifa18$PreferredPosition, c("CM","CAM","CDM", "LM", "RM" ), newLabel = 'MidFielder')
DataFifa18$PreferredPosition <- combineLevels(DataFifa18$PreferredPosition, c("CB","LWB","RWB","LB", "RB" ), newLabel = 'Defender') 

table(DataFifa18$PreferredPosition)
names(DataFifa18)

```
Removing columns which had positions which are not in our data now.

```{r}
DataFifa18 <- DataFifa18[, -c(4, 8:24, 26:37)]
names(DataFifa18)
str(DataFifa18)
```
DataSet is cleaned and we have all the columns which we will be requiring 
Now will be applying the Models for the analysis.
```{r}
# install.packages("randomForest")
library(randomForest)
head(DataFifa18)

```
Splitting Dataset in 70:30 as Train and Validation set. also creating Test Dataset.
```{r}
set.seed(100)
s <- sample(nrow(DataFifa18), 0.7 * nrow(DataFifa18), replace = FALSE)
train <- DataFifa18[s, ]
test <- DataFifa18[-s, ]

```
Now we will create Random Forest Model
```{r}
modelRF <- randomForest(PreferredPosition ~ ., data= train, importance = TRUE  )
str(modelRF)
```

#Copying predicted values from model to a new variable
```{r}
predPosTrain <- modelRF$predicted

library(caret)
confusionMatrix(predPosTrain, train$PreferredPosition)
```
```{r}
predPosTest <- predict(modelRF, newdata = test)
confusionMatrix(predPosTest, test$PreferredPosition)
```



Fitting Logistic Regression to the Training set.[ ## performing backward selection and removing insignificant variables as per p value]
```{r}
library(nnet)
modelLC = multinom(PreferredPosition ~ ., data = train)
summary(modelLC)

```

```{r}
predPosTrainLC <- predict(modelLC, newdata = train, type = "class" )

confusionMatrix(predPosTrainLC, train$PreferredPosition)

```

```{r}
predPosTestLC <- predict(modelLC, newdata = test, type = "class" )

confusionMatrix(predPosTestLC, test$PreferredPosition)
```
